### 2022-05-12 supplement.Rmd
Add robustness checks for gender model

```{r, trim_fill_selection}
# Re-fit frequentist meta-analysis using a two-level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# Run trim-and-fill analysis
res_trim_fill <- trimfill(res_freq_2)
print(res_trim_fill)

# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
res_selection_weights <- selmodel(
  res_freq_2,
  type = "stepfun", steps = c(0.01, .05, .3, 1)
)
print(res_selection_weights)

# More selection models based on four different step functions
tibble(
  delta_one_tailed_moderate = c(
    1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
    0.50, 0.50, 0.50, 0.50, 0.50, 0.50
  ),
  delta_one_tailed_severe = c(
    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
    0.30, 0.25, 0.10, 0.10, 0.10, 0.10
  ),
  delta_two_tailed_moderate = c(
    1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
    0.75, 0.80, 0.90, 0.95, 0.99, 1.00
  ),
  delta_two_tailed_severe = c(
    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
    0.50, 0.60, 0.75, 0.90, 0.99, 1.00
  )
) %>%
  print() %>%
  map(function(delta) {
    selmodel(
      res_freq_2,
      type = "stepfun",
      steps = c(
        0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
        0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
      ),
      delta = delta
    )
  }) -> res_selection_steps
print(res_selection_steps)
```

```{r, tabs8, include=TRUE}
# Combine all trim-and-fill and selection models into one table
tibble(
  res = c(
    list(res_freq_2, res_trim_fill, res_selection_weights), res_selection_steps
  ),
  label_1 = c(
    "Two-level model", "Trim-and-fill model",
    "Selection models:", "", "", "", ""
  ),
  label_2 = c(
    "", "", "Weight function [.01, .05, .30]",
    "One-tailed, moderate bias", "One-tailed, severe bias",
    "Two-tailed, moderate bias", "Two-tailed, severe bias"
  )
) %>%
  pmap_dfr(
    ~ print_res_freq_table(
      res_freq = ..1, label_1 = ..2, label_2 = ..3,
      label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
    )
  ) %>%
  select(-Parameter) %>%
  rename(`Hedges' $g$` = Estimate) -> tab_trim_fill_selection

# Save the table
write_csv(
  tab_trim_fill_selection,
  file = here(tables_dir, "trim_fill_selection.csv")
)

# Display the table
apa_table(
  tab_trim_fill_selection,
  align = "llccccc",
  caption = "Trim-and-fill and selection model analyses",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, figs4, include=TRUE, fig.width=6, fig.height=3.5, out.width="50%"}
# Compute new funnel, taking into account the trim-and-fill results
funnel_trim_fill <- with(
  list(
    z_crit_05 = stats::qnorm(0.975),
    max_se = max(sqrt(res_trim_fill$vi)) + 0.05
  ),
  {
    data.frame(
      x = c(
        res_trim_fill$b - z_crit_05 * sqrt(max_se^2),
        res_trim_fill$b,
        res_trim_fill$b + z_crit_05 * sqrt(max_se^2)
      ),
      y = c(max_se, 0, max_se)
    )
  }
)

# Create new funnel plot, enhanced by the filled in studies
trim_fill_color <- "#e42536"
plots_funnel[[1]] +
  # Add trim and fill funnel
  geom_path(
    data = funnel_trim_fill,
    aes(x = x, y = y),
    color = trim_fill_color
  ) +
  geom_vline(xintercept = res_trim_fill$b, color = trim_fill_color) +
  # Add filled in studies
  geom_point(
    data = with(res_trim_fill, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
    color = trim_fill_color, shape = 0
  )

# Save the plot
ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 6, height = 3.5)
```

```{r, trim_and_fill_gender}
dat <- dat_gender

# random-effects 2 level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_trim_fill <- trimfill(res_freq_2)
print(res_trim_fill)
# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_trim_fill$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_trim_fill$yi, vi = sqrt(res_trim_fill$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

# Save the plot
ggsave(here(figures_dir, "funnel_taf.pdf"), width = 5.56, height = 3.5)
```

```{r,selection_models_gender}
# random-effects 2 level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod <- selmodel(res_freq_2, type = "stepfun", steps = c(0.01, .05, .3, 1), verbose = TRUE)
print(sel_mod)
# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00)
)

sel_moderateonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.1, verbose = TRUE)
sel_severeonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.1, verbose = TRUE)
sel_moderatetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.2, verbose = TRUE)
sel_severetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.2, verbose = TRUE)

print(sel_moderateonetailed)
print(sel_severeonetailed)
print(sel_moderatetwotailed)
print(sel_severetwotailed)

# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
# print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
# print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
```

```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
    "Selection model: severe two-tailed"
  ),
  list(
    res_freq_2,
    res_trim_fill,
    sel_mod,
    sel_moderateonetailed,
    sel_severeonetailed,
    sel_moderatetwotailed,
    sel_severetwotailed
  ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Display the table
apa_table(
  tab_freq,
  align = "llccccc",
  caption = "Sensitivity/robustness analyses frequentist",
  font_size = "scriptsize",
  escape = FALSE
)

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq_gender.csv"))
```

>>>>

```{r, trim_fill_selection, include=TRUE}
# Re-fit the two frequentist meta-analyses using a two-level model
# This is because `rma.mv()` is not supported for trim-and-fill/selection models
list(meta = dat, gender = dat_gender) %>%
  map(function(x) rma.uni(gi, vi, data = x)) -> res_freq_2_lvl

# Trim-and-fill analysis
res_freq_2_lvl %>% map(trimfill) -> res_trim_fill

# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
res_freq_2_lvl %>%
  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
res_selection_weights

# More selection models based on four different step functions
res_freq_2_lvl %>%
  map(function(res) {

    # Define custom step functions
    tibble(
      delta_one_tailed_moderate = c(
        1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
        0.50, 0.50, 0.50, 0.50, 0.50, 0.50
      ),
      delta_one_tailed_severe = c(
        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
        0.30, 0.25, 0.10, 0.10, 0.10, 0.10
      ),
      delta_two_tailed_moderate = c(
        1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
        0.75, 0.80, 0.90, 0.95, 0.99, 1.00
      ),
      delta_two_tailed_severe = c(
        1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
        0.50, 0.60, 0.75, 0.90, 0.99, 1.00
      )
    ) %>%
      # Fit selection model for every step function
      map(function(delta) {
        selmodel(
          res,
          type = "stepfun",
          steps = c(
            0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
            0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
          ),
          delta = delta
        )
      })
  }) -> res_selection_steps

# Create seperate tables for the two different meta-analyses (rotation/gender)
# Each table will contain the results of all trim-and-fill and selection models
map(names(res_freq_2_lvl), function(name) {

  # Combine two-level, trim-and-fill, and selection models
  tibble(
    res = c(
      list(
        res_freq_2_lvl[[name]],
        res_trim_fill[[name]],
        res_selection_weights[[name]]
      ),
      res_selection_steps[[name]]
    ),
    label_1 = c(
      "Two-level model", "Trim-and-fill model",
      "Selection models:", "", "", "", ""
    ),
    label_2 = c(
      "", "", "Weight function [.01, .05, .30]",
      "One-tailed, moderate bias", "One-tailed, severe bias",
      "Two-tailed, moderate bias", "Two-tailed, severe bias"
    )
  ) %>%
    # Combine and format as a table
    pmap_dfr(
      ~ print_res_freq_table(
        res_freq = ..1, label_1 = ..2, label_2 = ..3,
        label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
      )
    ) %>%
    select(-Parameter) %>%
    rename(`Hedges' $g$` = Estimate)
}) %>%
  set_names(names(res_freq_2_lvl)) -> tabs_trim_fill_selection

# Save the tables
write_csv(
  tabs_trim_fill_selection$meta,
  file = here(tables_dir, "trim_fill_selection_meta.csv")
)
write_csv(
  tabs_trim_fill_selection$gender,
  file = here(tables_dir, "trim_fill_selection_gender.csv")
)

# Display the tables
apa_table(
  tabs_trim_fill_selection$meta,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
  font_size = "scriptsize",
  escape = FALSE
)
apa_table(
  tabs_trim_fill_selection$gender,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, figs4, include=TRUE, fig.width=12, fig.height=3.5}
# Create new funnel plots that take the trim-and-fill results into account
map2(res_trim_fill, plots_funnel, function(res, plot) {

  # Compute new funnel
  funnel_trim_fill <- with(
    list(
      z_crit_05 = stats::qnorm(0.975),
      max_se = max(sqrt(res$vi)) + 0.05
    ),
    {
      data.frame(
        x = c(
          res$b - z_crit_05 * sqrt(max_se^2),
          res$b,
          res$b + z_crit_05 * sqrt(max_se^2)
        ),
        y = c(max_se, 0, max_se)
      )
    }
  )

  # Add new funnel on top of the original funnel plot
  trim_fill_color <- "#e42536"
  plot +
    # Add trim and fill funnel
    geom_path(
      data = funnel_trim_fill,
      aes(x = x, y = y),
      color = trim_fill_color
    ) +
    geom_vline(xintercept = res$b, color = trim_fill_color) +
    # Add filled in studies
    geom_point(
      data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
      color = trim_fill_color, shape = 0
    )
}) -> plots_funnel_trim_fill

# Combine plots and legend
plot_grid(
  plotlist = plots_funnel_trim_fill, nrow = 1, labels = "auto",
  label_size = 11, label_fontfamily = "Helvetica"
) +
  draw_plot(legend_funnel, x = -0.39, y = 0.355)

# Save the plot
ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 12, height = 3.5)
```
